POMDP comparisons across sigma_m, sigma_g

### 2017-12-29 appendix/appendixB_99.Rmd
script

```{r}
options(mc.cores = parallel::detectCores()) # Reserve ~ 10 GB per core
log_dir <- "pomdp_historical"
```

```{r}
## Classic Graham-Schaefer. Note that recruitment occurs *before* harvest
gs <- function(r,K){
  function(x, h){ 
    x + x * r * (1 - x / K) - pmin(x,h)
  }
}
reward_fn <- function(x,h) pmin(x,h)
discount <- .95
```

@@

      sarsop(models[[i]]$transition,
             models[[i]]$observation,
             models[[i]]$reward,
             discount = discount,
             precision = 2e-6,
             timeout = 20000,
             log_dir = log_dir,
             log_data = log_data)
    })
)

>>>>

```{r}
options(mc.cores = 3) # Reserve ~ 10 GB per core
log_dir <- "pomdp_historical"
```

```{r}
## Classic Graham-Schaefer. Note that recruitment occurs *before* harvest
gs <- function(r,K){
  function(x, h){ 
    x + x * r * (1 - x / K) - pmin(x,h)
  }
}
reward_fn <- function(x,h) pmin(x,h)
discount <- .99
```

@@

      sarsop(models[[i]]$transition,
             models[[i]]$observation,
             models[[i]]$reward,
             discount = discount,
             precision = 2e-6,
             timeout = 70000,
             log_dir = log_dir,
             log_data = log_data)
    })
)

### 2017-12-29 appendix/appendix_99.Rmd
script

```{r}
reward_fn <- function(x,h) pmin(x,h)
discount <- 0.95
```

@@

```{r eval=TRUE}
dir.create(log_dir)
options(mc.cores=9)

@@

      sarsop(models[[i]]$transition,
             models[[i]]$observation,
             models[[i]]$reward,
             discount = discount,
             precision = 0.00000002,
             timeout = 15000,
             log_dir = log_dir,
             log_data = log_data)
    })
)

>>>>

```{r}
reward_fn <- function(x,h) pmin(x,h)
discount <- 0.99
```

@@

```{r}
options(mc.cores=3)
```

```{r eval=TRUE}
dir.create(log_dir)

@@

      sarsop(models[[i]]$transition,
             models[[i]]$observation,
             models[[i]]$reward,
             discount = discount,
             precision = 0.00000002,
             timeout = 60000,
             log_dir = log_dir,
             log_data = log_data)
    })
)
